Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-10 WSSSPE2_report/WSSSPE2_review.tex
Section 2: fix a typo.

WSSSPE1 was organized into sessions, each of which was aimed at discussing one
or more of the themes from the call for papers, with a few paper authors invited
to summarize the other papers in that them as a panel, followed by general
discussion about that theme. The mapping of papers to themes was done by the
organizers.

>>>>

WSSSPE1 was organized into sessions, each of which was aimed at discussing one
or more of the themes from the call for papers, with a few paper authors invited
to summarize the other papers in them as a panel, followed by general
discussion about that theme. The mapping of papers to themes was done by the
organizers.
